---
title: "Script3_CombinedAnalysis"
author: "Christopher LeBoa"
date: "2025-06-27"
output: html_document
---

The purpose of this script is to combine the microbiological data with the survey data collected from households in order to understand 

1) The relationship with pathogen data (log transformed E.coli) and WASH variables 

2) Conduct a linear regression relating potential exposures with amount of e.coli as outcome variable 

3) Make a single table of different regression results using the package Kable


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#Load packages
#install.packages("knitr")

library(tidyverse)
library(knitr)
library(here)

here()

# Load the data
taqman_data <- read_csv(here("clean_data", "tac_data_cleaned.csv"))
microbiological_data <- read_csv(here("clean_data", "microbial_data_cleaned.csv"))
survey_data <- read_csv(here("simulated_data", "survey_data_simulated.csv"))

```

## Combine Data 
We are going to combine the two datasets using the `household_id` as the key. This will allow us to analyze the relationship between the microbiological data and the survey data.

```{r cars}
combined_data <-survey_data %>% 
  left_join(microbiological_data, by = "household_id") 

#Independant task: Join the taqman data to this merged dataset

```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
